A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2017-01-25 doc/paper1-submission/paper5-adjusted.tex
Convert figures 1-7

\begin{figure}
\subfloat[Input tree 1]{\includegraphics[width=0.45\textwidth]{Figures__toy_ambig__abcd}

}\hfill{}\subfloat[Input tree 2]{\includegraphics[width=0.45\textwidth]{Figures__toy_ambig__bcde}

@@

\subfloat[Summary tree]{\includegraphics[width=0.45\textwidth]{Figures__toy_ambig__soln1}

}\hfill{}\subfloat[Summary tree]{\includegraphics[width=0.45\textwidth]{Figures__toy_ambig__soln2}

@@

\begin{figure}
\subfloat[Input tree 1]{\includegraphics[scale=0.57]{Figures__toy_pairwise_compat__abc}

}\hfill{}\subfloat[Input tree 2]{\includegraphics[scale=0.57]{Figures__toy_pairwise_compat__acd}

}\hfill{}\subfloat[Input tree 3]{\includegraphics[scale=0.57]{Figures__toy_pairwise_compat__bcd}

@@

\subfloat[Summary tree]{\includegraphics[scale=0.57]{Figures__toy_pairwise_compat__s12}

}\hfill{}\subfloat[Summary tree]{\includegraphics[scale=0.57]{Figures__toy_pairwise_compat__s13}

}\hfill{}\subfloat[Summary tree]{\includegraphics[scale=0.57]{Figures__toy_pairwise_compat__s23}

@@

Propinquity was designed to function as a part of the Open Tree of
Life software architecture, so the first few steps of the pipeline
involve transforming artifacts from that project into a set of rooted
trees and a phylogenetic taxonomy. The phylesystem API \citep{McTavishEtAt2015}
of Open Tree allows users to curate published estimates of trees and
create ranked collections of these trees. Early steps in the propinquity
pipeline manipulate the phylogenetic input trees to improve their
usability and reliability. The first steps of the pipeline (see Fig.
\ref{fig:pipeline}) collect a list of trees to include (in the \texttt{phylo\_input}
subdirectory) and store copies of these files (in the \texttt{phylo\_snapshot}
subdirectory) to make it easier to replicate the operation (because
the collection of trees and the tree files change due to curation).
\begin{figure}
\begin{centering}
\includegraphics[height=0.70\paperheight]{pipeline-tools.pdf}
\par\end{centering}
\caption{Organization of the \emph{propinquity} pipeline. Each colored pentagon
labels a program (blue for otcetera-based tools and red for python
scripts in the propinquity or peyotl repository) that performs the
important operations in each step; the number before the tool name
refers to the section in this paper that describes the operation.
The output of each step corresponds to a subdirectory of the propinquity
system which will hold the output artifacts for the step. Ovals are
resources that are required (OTT and Open Tree's phylesystem repository).
White pentagons are user-controlled inputs.}
\label{fig:pipeline}
\end{figure}

@@

\begin{figure}
\subfloat[Tree 1]{\includegraphics[scale=0.4]{Figures__cleaned_phylo__ex_2@tree1\lyxdot tre}

}\hfill{}\subfloat[Tree 2]{\includegraphics[scale=0.4]{Figures__cleaned_phylo__ex_2@tree2\lyxdot tre}

}\hfill{}\subfloat[Taxonomy Tree]{\includegraphics[scale=0.4]{Figures__cleaned_ott__cleaned_ott\lyxdot tre}

@@

\begin{figure}
\subfloat[Tree 1]{\includegraphics[scale=0.4]{Figures__exemplified_phylo__ex_2@tree1\lyxdot tre}

}\hfill{}\subfloat[Tree 2]{\includegraphics[scale=0.4]{Figures__exemplified_phylo__ex_2@tree2\lyxdot tre}

}\hfill{}\subfloat[Pruned taxonomy tree $\protect\prunedTaxonomy$]{\includegraphics[scale=0.4]{Figures__exemplified_phylo_taxonomy_uncontested\lyxdot tre}

@@

\begin{figure}
  \subfloat[Subproblem \emph{ABCD}]{\includegraphics[width=0.3\textwidth]{Figures__subproblems__14__1\lyxdot tre}%
    \hfill{}\includegraphics[width=0.3\textwidth]{Figures__subproblems__14__2\lyxdot tre}%
    \hfill{}\includegraphics[width=0.3\textwidth]{Figures__subproblems__14__3\lyxdot tre}

@@

  \subfloat[Subproblem \emph{root}]{\includegraphics[width=0.3\textwidth]{Figures__subproblems__17__1\lyxdot tre}%
    \hfill{}\includegraphics[width=0.3\textwidth]{Figures__subproblems__17__2\lyxdot tre}%
    \hfill{}\includegraphics[width=0.3\textwidth]{Figures__subproblems__17__3\lyxdot tre}

@@

\caption{Subproblems generated from the exemplified trees shown in Fig. \ref{fig:exemplify-example}.
A trivial statement from the first tree that a taxon labelled $ABCD$
is sister to $E$ has been omitted, because trees with only 2 leaves
do not contain phylogenetic information.
Similarly, the trivial problems that list E1 and F1 as the only daughters
of taxa E and F have been omitted.}
\label{fig:subproblems-example}
\end{figure}
\begin{figure}
\subfloat[]{\includegraphics[scale=0.57]{Figures__uncontested_worsens_score__ab1c}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Figures__uncontested_worsens_score__acb2}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Figures__uncontested_worsens_score__tax}

@@

\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Figures__uncontested_worsens_score__opt}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Figures__uncontested_worsens_score__returned}

>>>>

\begin{figure}
\subfloat[Input tree 1]{\includegraphics[width=0.45\textwidth]{Fig1a}

}\hfill{}\subfloat[Input tree 2]{\includegraphics[width=0.45\textwidth]{Fig1b}

@@

\subfloat[Summary tree]{\includegraphics[width=0.45\textwidth]{Fig1c}

}\hfill{}\subfloat[Summary tree]{\includegraphics[width=0.45\textwidth]{Fig1d}

@@

\begin{figure}
\subfloat[Input tree 1]{\includegraphics[scale=0.57]{Fig2a}

}\hfill{}\subfloat[Input tree 2]{\includegraphics[scale=0.57]{Fig2b}

}\hfill{}\subfloat[Input tree 3]{\includegraphics[scale=0.57]{Fig2c}

@@

\subfloat[Summary tree]{\includegraphics[scale=0.57]{Fig2d}

}\hfill{}\subfloat[Summary tree]{\includegraphics[scale=0.57]{Fig2e}

}\hfill{}\subfloat[Summary tree]{\includegraphics[scale=0.57]{Fig2f}

@@

Propinquity was designed to function as a part of the Open Tree of
Life software architecture, so the first few steps of the pipeline
involve transforming artifacts from that project into a set of rooted
trees and a phylogenetic taxonomy. The phylesystem API \citep{McTavishEtAt2015}
of Open Tree allows users to curate published estimates of trees and
create ranked collections of these trees. Early steps in the propinquity
pipeline manipulate the phylogenetic input trees to improve their
usability and reliability. The first steps of the pipeline (see Fig.
\ref{fig:pipeline}) collect a list of trees to include (in the \texttt{phylo\_input}
subdirectory) and store copies of these files (in the \texttt{phylo\_snapshot}
subdirectory) to make it easier to replicate the operation (because
the collection of trees and the tree files change due to curation).
\begin{figure}
\begin{centering}
\includegraphics[height=0.70\paperheight]{Fig3.pdf}
\par\end{centering}
\caption{Organization of the \emph{propinquity} pipeline. Each colored pentagon
labels a program (blue for otcetera-based tools and red for python
scripts in the propinquity or peyotl repository) that performs the
important operations in each step; the number before the tool name
refers to the section in this paper that describes the operation.
The output of each step corresponds to a subdirectory of the propinquity
system which will hold the output artifacts for the step. Ovals are
resources that are required (OTT and Open Tree's phylesystem repository).
White pentagons are user-controlled inputs.}
\label{fig:pipeline}
\end{figure}

@@

\begin{figure}
\subfloat[Tree 1]{\includegraphics[scale=0.4]{Fig4a}

}\hfill{}\subfloat[Tree 2]{\includegraphics[scale=0.4]{Fig4b}

}\hfill{}\subfloat[Taxonomy Tree]{\includegraphics[scale=0.4]{Fig4c}

@@

\begin{figure}
\subfloat[Tree 1]{\includegraphics[scale=0.4]{Fig5a}

}\hfill{}\subfloat[Tree 2]{\includegraphics[scale=0.4]{Fig5b}

}\hfill{}\subfloat[Pruned taxonomy tree $\protect\prunedTaxonomy$]{\includegraphics[scale=0.4]{Fig5c}

@@

\begin{figure}
  \subfloat[Subproblem \emph{ABCD}]{\includegraphics[width=0.3\textwidth]{Fig6a}%
    \hfill{}\includegraphics[width=0.3\textwidth]{Fig6b}%
    \hfill{}\includegraphics[width=0.3\textwidth]{Fig6c}

@@

  \subfloat[Subproblem \emph{root}]{\includegraphics[width=0.3\textwidth]{Fig6d}%
    \hfill{}\includegraphics[width=0.3\textwidth]{Fig6e}%
    \hfill{}\includegraphics[width=0.3\textwidth]{Fig6f}

@@

\caption{Subproblems generated from the exemplified trees shown in Fig. \ref{fig:exemplify-example}.
A trivial statement from the first tree that a taxon labelled $ABCD$
is sister to $E$ has been omitted, because trees with only 2 leaves
do not contain phylogenetic information.
Similarly, the trivial problems that list E1 and F1 as the only daughters
of taxa E and F have been omitted.}
\label{fig:subproblems-example}
\end{figure}
\begin{figure}
\subfloat[]{\includegraphics[scale=0.57]{Fig7a}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Fig7b}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Fig7c}

@@

\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Fig7d}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Fig7e}
